Determinism, Complexity, and Predictability in Computer Performance

### 2014-08-01 results.tex
fixed end of JG paragraph

The discussion in the previous paragraph highlights the second finding
of this paper: the ability of our proposed heuristic to flag
inappropriate models.  \arima is an automated, mechanical procedure
for choosing parameters for an ARIMA model of a given data set.  While
the tests and criteria employed by this algorithm are sophisticated
(see Section~\ref{sec:arima}), the results can still be
sub-optimal---if the initial space of models being searched is not
broad enough, for instance, or if one of the preliminary tests gives
an erroneous result.  \arima \emph{always} returns a model, and it can
be very hard to detect when that model is bad.  Our results suggest a
way to do so: if the MASE score of an \arima model is out of line with
the WPE value, that can be an indication of inappropriateness in the
order selection and parameter estimation procedure.  By examining the
\arima MASE scores vs. WPE values of \col, we were able to see that,
while all signal complexities were the same, some of the signals had
much higher MASE values. This suggested to us inappropriate parameter
selection for these time series. We then went back and manually
assisted the automated fitting procedure, resulting in models with
consistent MASE vs WPE score, and improved forecasts.

>>>>

The discussion in the previous paragraph highlights the second finding
of this paper: the ability of our proposed heuristic to flag
inappropriate models.  \arima is an automated, mechanical procedure
for choosing parameters for an ARIMA model of a given data set.  While
the tests and criteria employed by this algorithm are sophisticated
(see Section~\ref{sec:arima}), the results can still be
sub-optimal---if the initial space of models being searched is not
broad enough, for instance, or if one of the preliminary tests gives
an erroneous result.  \arima \emph{always} returns a model, and it can
be very hard to detect when that model is bad.  Our results suggest a
way to do so: if the MASE score of an auto-fitted model like \arima is
out of line with the WPE value of the data, that can be an indication
of inappropriateness in the order selection and parameter estimation
procedure.  A close examination of the \arima MASE scores and WPE
values of the 15 \col traces, for instance, brought out such a
situation: all of these signals had the same complexity, but some (the
outliers in the blue cluster of $+$ points in the bottom-left panel of
Figure~\ref{fig:what}) had much higher \arima MASE values, indicating
a failure in the \arima process.  We then went back and manually
assisted the automated fitting procedure---forcing inclusion of a term
that is appropriate for a nonstationary signal.  In all cases, this
produced ARIMA models with MASE scores in line with the others in that
cluster.
